---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = F,
  warning = F
)
library(magrittr)
```

# ZoomReports

The goal of ZoomReports is to gain more insight from the reports we get after a Zoom webinar.

## Installation

``` r
devtools::install_github('beemyfriend/ZoomReports')
```

## Where to get the Zoom Attendee Report

If you hosted a webinar, then you can get the associated reports by logging into [zoom.us](https://zoom.us) and then going to [zoom.us/account/report/webinar](https://zoom.us/account/report/webinar)

## Example

First, let's load the package.

```{r}
library(ZoomReports)
```

We provide an example of a typical **attendee report** provided after a Zoom Webinar. 

```{r example}
attend <- system.file("extdata",
                      "Anonymized_Zoom_Attendee_Report.csv",
                      package = "ZoomReports" )
```

```{r, echo = F}
attend %>%
  readLines() %>%
  head(10)
```

This single file contains 5 seperate CSV datasets: **Attendee Report**, **Host Details**, **Panelist Details**, **Attendee Details**, and **Other Details**. We are only interested in the data contained in **Attendee Details**.

```{r}
attendees <- getAttendees(attend)
```

```{r, echo=F}
attendees %>%
  head(3) %>%
  knitr::kable()
```

We can use this data to examine the country of our attendees.

```{r}
countries <- getCountryInfo(attendees)
```

```{r, echo = F}
countries %>%
  dplyr::arrange(desc(Attendees)) %>%
  head() %>%
  knitr::kable()
```

Now let's look at the amount of attendees that joined or left the webinar over either 1 minute intervals or 10 minute intervals.

```{r}
start_time <- "2020-03-28 08:00"
end_time <- "2020-03-28 18:00"

intervals_01 <- createIntervals(start_time, end_time, 1)
intervals_10 <- createIntervals(start_time, end_time, 10)
```

The output of `createIntervals` is simply a vector of time intervals. 

```{r echo = F}
head(intervals_10, 7)
```

We can use this to bin the number of attendees that either join or leave during that interval.

```{r}
timeData_01 <- getTimeData(intervals_01, attendees)
timeData_10 <- getTimeData(intervals_10, attendees)
```

```{r, echo = F}
timeData_10 %>%
  head() %>%
  knitr::kable()
```

With this time data we an now create visualizations to see the flow of people throughout the webinar.

```{r}
showAttendeeMovement(timeData_01, 'cumulative')
```

```{r}
showAttendeeMovement(timeData_10, 'discrete')
```

```{r}

showAttendeeMovement(timeData_10, 'breakdown')
```
